Optimizing a PoS Tag Set for Dependency Parsing

### 2016-05-05 submission.tex
la til abstract

\begin{document}
\maketitle
\begin{abstract}
Abstraction ensues.
\end{abstract}

>>>>

\begin{document}
\maketitle
\begin{abstract}

This paper reports on a suite of experiments that evaluates how the linguistic
granularity of part-of-speech tag sets impacts the performance of tagging and
syntactic dependency parsing. Our results show that parsing accuracy can be
significantly improved by introducing more fine-grained morphological
information in the tag set, even when tagger accuracy goes down as a result of
the increased complexity of the tagging task. Our taggers and parsers are
trained and tested using the annotations of the Norwegian Dependency Treebank.

\end{abstract}
